%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}


%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
Professor Peter D. Adams \\
\emph{Aging Cell} Editor-in-Chief \\
Sanford Burnham Medical Discovery Institute \\
10901 North Torrey Pines Rd \\
La Jolla, CA 92037, USA\\}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------
\iffalse
\begin{center}
\large\bf Dr. Danila Bobkov \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
4 Tikhoretsky\\ St-Petersburg, Russia 195251 \\ (999) 043-5439 % Your address and phone number
\end{center}
\vfill
\fi
\signature{Dr. Danila Bobkov \\
Institute of Cytology RAS \\
4 Tikhoretsky ave. \\
St-Petersburg, 194064, Russia \\
Tel. :+7(999) 043-5439 \\
E-mail: bobkov@incras.ru} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Mr. Adams,}

I am submitting a manuscript for consideration of publication in \emph{Aging Cell}.
The manuscript is entitled “Cytoskeletal and motility changes in human umbilical cord mesenchymal stem cells associated with nuclear-cytoplasmic RhoА redistribution during replicative senescence”.

It has not been published elsewhere and it has not been submitted simultaneously for publication elsewhere.

The work is devoted to the analysis of the contractile apparatus and mobility characteristics of mesenchymal stem cells obtained from the human umbilical cord.

Since we are investigating the process of replicative aging in this cells, by the means of long-term cultivation (up to 36 passage), it seems to me quite appropriate to publish our work in the scope of \emph{Aging Cell} interests.

I think that the data relating to a detailed statistical analysis of various colocalization coefficients obtained by calculating the results of immunofluorescence may be of some independent interest, so I allowed myself to accompany the manuscript with an application with additional tables and graphs.

Thank you very much for your consideration.

\closing{Sincerely yours, }


\encl{Manuscript, supplementary materials} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
